Retrofitting Effect Handlers onto OCaml

### 2020-11-20 retro-concurrency.tex
Applied KCs change to conclusion for wording on fibers/effects

Our design for effect handlers in OCaml walks the tightrope of maintaining
compatibility (for profiling, debuggers and negligible overheads for existing
programs), while unlocking the full power of non-local control flow constructs.
Our evaluation shows that we have achieved our goal: we retain compatibility
with a surprisingly low performance overhead for sequential code that preserves
the spirit of ``fast exceptions'' that has always characterised OCaml
programming. We believe that the introduction of first-class fibres and effects
into OCaml -- along with a parallel runtime~\cite{Sivaramakrishnan20} -- will
open OCaml to highly task-parallel applications with minimal hit to sequential
performance.

>>>>

Our design for effect handlers in OCaml walks the tightrope of maintaining
compatibility (for profiling, debuggers and negligible overheads for existing
programs), while unlocking the full power of non-local control flow constructs.
Our evaluation shows that we have achieved our goal: we retain compatibility
with a surprisingly low performance overhead for sequential code that preserves
the spirit of ``fast exceptions'' that has always characterised OCaml
programming. We believe that the introduction of lightweight fibers to support
effect handlers into OCaml -- along with a parallel
runtime~\cite{Sivaramakrishnan20} -- will open OCaml to highly task-parallel
applications with minimal hit to sequential performance.
